Model Comparison

### 2020-02-11 stats/model_comparison.Rmd
fix model comparison chunk

@@

  test_prag %>%
    right_join(d_model_comp)%>%
    mutate(id = 1:length(pred))%>%
    select(id, model,chain,iteration, age, alignment,item,pred, correct),

  test_global %>%
    right_join(d_model_comp)%>%
    mutate(id = 1:length(pred))%>%
    select(id, model,chain,iteration, age, alignment,item,pred, correct),

   test_flat %>%
    right_join(d_model_comp)%>%
    mutate(id = 1:length(pred))%>%
    select(id, model,chain,iteration, age, alignment,item,pred, correct)
)%>%
  mutate(log_like = log(ifelse(correct == 1, pred, 1 - pred)))%>% # calculate log likelihood
  select(-pred, - correct)%>%
  spread(model, log_like)%>%
  mutate(prag_vs_global = pragmatic - global, # subtract likelihood for each predictions and model
         prag_vs_flat= pragmatic - flat,
         global_vs_flat = global - flat) %>%
  summarise(prag_vs_global = sum(prag_vs_global), # sum up likelihood difference to get log Bayes factor
            prag_vs_flat = sum(prag_vs_flat),
            global_vs_flat = sum(global_vs_flat))%>%
  gather(model, logBF)

>>>>

d_model_comp.summarized <- d_model_comp %>% 
  group_by(alignment, item, age) %>% 
  summarize(n=n(), k = sum(correct))

@@

  test_prag %>%
    right_join(d_model_comp.summarized) %>%
    mutate(id = 1:length(pred))%>%
    select(id, model,chain,iteration, age, alignment,item,pred, n, k),

  test_global %>%
    right_join(d_model_comp.summarized)%>%
    mutate(id = 1:length(pred))%>%
    select(id, model,chain,iteration, age, alignment,item,pred, n, k),

   test_flat %>%
    right_join(d_model_comp.summarized)%>%
    mutate(id = 1:length(pred))%>%
    select(id, model,chain,iteration, age, alignment,item,pred, n, k)
) %>%
  mutate(
    log_like = dbinom(x = k, size = n, prob = pred, log = TRUE)
  ) %>%
  group_by(chain, model, iteration) %>%
  summarize(total_likelihood_sample = sum(log_like)) %>%
  group_by(chain, model) %>%
  summarize(marginal_likelihood = matrixStats::logSumExp(total_likelihood_sample)) %>%
  spread(model, marginal_likelihood) %>%
  mutate(prag_vs_global = pragmatic - global, # subtract likelihood for each predictions and model
         prag_vs_flat= pragmatic - flat,
         global_vs_flat = global - flat) %>%
  select(-pragmatic, -global, -flat) %>%
  gather(model, logBF, -chain)
